Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-22 paper/tex/appendix.tex
revise to address mroe Seth comments

``Stacking'' according to
\begin{equation}
  \label{eq:stacked}
  \hat{N}^{H}(z) \equiv \frac{1}{N_{tot}}\ \sum_{i}^{N_{tot}}\ \hat{p}^{H}_{i}(z)
\end{equation}
 is the most widely used method for obtaining $\hat{N}^{H}(z)$ as an estimator of the redshift distribution from \pzpdf s derived by a method $H$. While the stacked estimator of the redshift distribution violates the mathematical definition of statistical independence and is thus not formally correct\footnote{\citet{Malz:chippr} shows how the stacking procedure can lead to bias in the estimate of $N(z)$ and presents a principled alternative to this commonly employed method.}, we use it as a basis for comparison of \pzpdf\ methods under the untested assumption that the response of our metrics of $\hat{N}^{H}(z)$ will be analogous to the same metrics applied to a principled estimator of the redshift distribution.

>>>>

``Stacking'' according to
\begin{equation}
  \label{eq:stacked}
  \hat{N}^{H}(z) \equiv \frac{1}{N_{tot}}\ \sum_{i}^{N_{tot}}\ \hat{p}^{H}_{i}(z)
\end{equation}
 is the most widely used method for obtaining $\hat{N}^{H}(z)$ as an estimator of the redshift distribution from \pzpdf s derived by a method $H$. While the stacked estimator of the redshift distribution violates the mathematical definition of statistical independence and is thus not formally correct\footnote{Malz \& Hogg (in prep) shows how the stacking procedure can lead to bias in the estimate of $N(z)$ and presents a principled alternative to this commonly employed method.  See \url{https://github.com/aimalz/chippr} for details.}, we use it as a basis for comparison of \pzpdf\ methods under the untested assumption that the response of our metrics of $\hat{N}^{H}(z)$ will be analogous to the same metrics applied to a principled estimator of the redshift distribution.

### 2019-11-22 paper/tex/discussion.tex
revise to address mroe Seth comments

The work presented in this paper is only a first step in assessing \pzpdf\ approaches and moving toward an improved photometric redshift estimator.
Here we discuss the next steps for subsequent investigations.

>>>>

The work presented in this paper is only a first step in assessing \pzpdf\ approaches and moving toward a photometric redshift estimator that will be employed for LSST analyses.
Here we discuss the next steps for subsequent investigations.

### 2019-11-22 paper/tex/methods.tex
address more Seth typos
revise to address mroe Seth comments

\begin{table*}  %%% DATA TABLE %%%
\caption{List of \pzpdf\ codes featured in this study} \label{tab:list_of_codes}\resizebox{\textwidth}{!}{
\begin{tabular}{lll}
\hline
\bf Published code & \bf Type & \bf Public source code \\
\hline
\lephare~\citep{Arnouts:99}	   & template fitting	& \url{http://www.cfht.hawaii.edu/~arnouts/lephare.html} \\
\bpz~\citep{Benitez:00} 		   & template fitting	& \url{http://www.stsci.edu/~dcoe/BPZ/} \\
\eazy~\citep{Brammer:08}		   & template fitting & \url{https://github.com/gbrammer/eazy-photoz} \\
\annz~\citep{Sadeh:16}		     & machine learning	& \url{https://github.com/IftachSadeh/ANNZ} \\
\flexzboost~\citep{Izbicki:17} & machine learning & \url{https://github.com/tpospisi/flexcode}; \url{https://github.com/rizbicki/FlexCoDE}\\
%\textsc{Frankenz} 	& ML 	& \citet{Speagle:frankenz}	& \url{https://github.com/joshspeagle/frankenz} \\
\gpz~\citep{Almosallam:15b}	   & machine learning	& \url{https://github.com/OxfordML/GPz} \\
\metaphor~\citep{Cavuoti:17}   & machine learning	& \url{http://dame.dsf.unina.it}\\
\cmnn~\citep{Graham:17}        & machine learning & N/A \\
\skynet~\citep{Graff:14}       & machine learning & \url{http://ccpforge.cse.rl.ac.uk/gf/project/skynet/} \\
\tpz~\citep{Carrasco_Kind:13}	 & machine learning	& \url{https://github.com/mgckind/MLZ} \\
\delight~\citep{Leistedt:17}   & hybrid           & \url{https://github.com/ixkael/Delight} \\
\hline
\trainz 	                             & machine learning	& See Section~\ref{sec:trainz} \\
\end{tabular}}
\end{table*}

@@

\gpz \citep{Almosallam:16a,Almosallam:15b} is a sparse Gaussian process-based code, a scalable approximation of full Gaussian Processes \citep{Rasmussen:06}, that produces input-dependent variance estimates corresponding to heteroscedastic noise.
The model assumes a Gaussian posterior probability $p(z \vert \x) = \mathcal{N}\left(z \vert \mu(\x), \sigma(\x)^{2}\right)$ of the output redshift $z$ given the input photometry $\x$.
The mean $\mu(\x)$ and the variance $\sigma(\x)^{2}$ are modeled as functions $f(\x) = \sum_{i=1}^{m}w_{i}\phi_{i}(\x)$ that are linear combinations of $m$ basis functions $\left\{\phi_{i}(\x)\right\}_{i=1}^{m}$ with associated weights $\left\{w_{i}\right\}_{i=1}^{m}$.
% Basis function models, for specific classes of basis functions such as the sigmoid or the squared exponential, have the advantage of being universal approximators, i.e. there exist a function of that form that can approximate any function, with mild assumptions, to any desired degree of accuracy.
The details on how to learn the parameters of the model and the hyper-parameters of the basis functions are described in \citet{Almosallam:15b}.
\gpz's variance estimate is composed of a model uncertainty term corresponding to sparsity of the training set photometry and a noise uncertainty term encompassing noisy photometric observations, enabling quantification of any need for more representative or more precise training samples.
\gpz\ may also weight training set samples by importance according to $|z_{\mathrm{spec}} - z_{\mathrm{phot}}| / (1+z_{\mathrm{spec}})$ to minimize the normalized \pz\ point estimate error.  However, this function may be adapted to \pzpdf s, pressuring the model to dedicate more resources to test set galaxies that are not well-represented in the training set.

>>>>

\begin{table*}  %%% DATA TABLE %%%
\caption{List of \pzpdf\ codes featured in this study} \label{tab:list_of_codes}\resizebox{\textwidth}{!}{
\begin{tabular}{lll}
\hline
\bf Published code & \bf Type & \bf Public source code \\
\hline
\bpz~\citep{Benitez:00} 		   & template fitting	& \url{http://www.stsci.edu/~dcoe/BPZ/} \\
\eazy~\citep{Brammer:08}		   & template fitting & \url{https://github.com/gbrammer/eazy-photoz} \\
\lephare~\citep{Arnouts:99}	   & template fitting	& \url{http://www.cfht.hawaii.edu/~arnouts/lephare.html} \\
\annz~\citep{Sadeh:16}		     & machine learning	& \url{https://github.com/IftachSadeh/ANNZ} \\
\cmnn~\citep{Graham:17}        & machine learning & N/A \\
\delight~\citep{Leistedt:17}   & hybrid           & \url{https://github.com/ixkael/Delight} \\
\flexzboost~\citep{Izbicki:17} & machine learning & \url{https://github.com/tpospisi/flexcode}; \url{https://github.com/rizbicki/FlexCoDE}\\
\gpz~\citep{Almosallam:15b}	   & machine learning	& \url{https://github.com/OxfordML/GPz} \\
\metaphor~\citep{Cavuoti:17}   & machine learning	& \url{http://dame.dsf.unina.it}\\
\skynet~\citep{Graff:14}       & machine learning & \url{http://ccpforge.cse.rl.ac.uk/gf/project/skynet/} \\
\tpz~\citep{Carrasco_Kind:13}	 & machine learning	& \url{https://github.com/mgckind/MLZ} \\
\hline
\trainz 	                             & machine learning	& See Section~\ref{sec:trainz} \\
\end{tabular}}
\end{table*}

@@

\gpz \citep{Almosallam:16a,Almosallam:15b} is a sparse Gaussian process-based code, a scalable approximation of full Gaussian Processes \citep{Rasmussen:06}, that produces input-dependent variance estimates corresponding to heteroscedastic noise.
The model assumes a Gaussian posterior probability $p(z \vert \x) = \mathcal{N}\left(z \vert \mu(\x), \sigma(\x)^{2}\right)$ of the output redshift $z$ given the input photometry $\x$.
The mean $\mu(\x)$ and the variance $\sigma(\x)^{2}$ are modeled as functions $f(\x) = \sum_{i=1}^{m}w_{i}\phi_{i}(\x)$ that are linear combinations of $m$ basis functions $\left\{\phi_{i}(\x)\right\}_{i=1}^{m}$ with associated weights $\left\{w_{i}\right\}_{i=1}^{m}$.
% Basis function models, for specific classes of basis functions such as the sigmoid or the squared exponential, have the advantage of being universal approximators, i.e. there exist a function of that form that can approximate any function, with mild assumptions, to any desired degree of accuracy.
The details on how to learn the parameters of the model and the hyper-parameters of the basis functions are described in \citet{Almosallam:15b}.
\gpz's variance estimate is composed of a model uncertainty term corresponding to sparsity of the training set photometry and a noise uncertainty term encompassing noisy photometric observations, enabling quantification of any need for more representative or more precise training samples.
\gpz\ may also weight training set samples by importance according to $|z_{\mathrm{spec}} - z_{\mathrm{phot}}| / (1+z_{\mathrm{spec}})$ to minimize the normalized \pz\ point estimate error.  However, this function may be adapted to \pzpdf s, adding weight to test set galaxies that are not well-represented in the training set.
